Dissonance-Santiago-v2-Word

### 2020-03-05 Dissonance_Santiago_v2/Dissonance_Santiago_v2_Word.Rmd
Created Word file for Beatriz

---
title: Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Subjective Wellbeing
author:
  - name: Author 1
    email: a1@university.com
    affiliation: Some University
    footnote: Corresponding Author
  - name: Author 2
    email: a2@school.com
    affiliation: Some School
address:
  - code: Some University
    address: Department, Street, City, State, Zip
  - code: Some School
    address: Department, Street, City, State, Zip
abstract: |
   **Introduction**  
   Subjective wellbeing is a topic that has attracted considerable attention in recent years due to the way it correlates with health. From a transportation perspective, there is a burgeoning literature on the way travel can impact subjective wellbeing, and how this, in turn, can influence behavior.  
   **Objective**  
   The objective of this paper is to analyze a number of affective values associated with subjective wellbeing and the modes of transportation that people commonly use. In particular, we are interested in the potential for dissonance with respect to the primary mode of travel.  
   **Materials and Methods**  
   The study is based on data collected from a sample of travellers in the city of Santiago, in Chile. Participants in the study were asked about their usual mode of travel, and then were asked to name the mode or modes that they associate with the affective values of freedom, enjoyment, happiness, poverty, luxury and status. Analysis is based on tests of independence and visualization via mosaic plots.  
   **Results**  
   The results indicate that users of public transportation experience the most dissonance in terms of affective values, and active travellers the least. For those travellers who experience dissonance, active travel is the mode most commonly associated with freedom, enjoyment, and happiness, public transportation is most commonly associated with poverty, and the automobil is most commonly associated with luxury and status.

   journal: "Journal of Transportation & Health"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article

header-includes:
   - \usepackage[margin=1in]{geometry}
   - \usepackage{lineno}
   - \linenumbers
---

<!-- This paper is an R markdown document that includes self-contained, reproducible analysis. To reproduce the paper the following files are needed:

1. Dissonance_Santiago_v1.Rmd (this R markdown document)

2. `Dissonance_Santiago.RData`. For reference: this data file was created using R notebook `00. Analysis of Dissonance Detailed.Rmd`. The initial analysis was done in the same R notebook. Neither of these two notebooks are needed for this document.

3. For compiling into a pdf in the style of an Elsevier document: elsarticle.cls, elsevier-harvard.csl, elsevier-harvard-without-titles.csl, elsevier-vancouver.csl, elsevier-without-titles.cls, elsevier-with-titles.csl, elsevier-with-titles-alphabetical.csl, mybibfile.bib
-->

>>>>

---
title: "Dissonance-Santiago-v2-Word"
author: "Antonio Paez"
date: "3/4/2020"
output: word_document
---
